How does increasing $s$ and $k$ effect log normalising constant estimation

### 2023-04-13 src/naomi-simple_increase-s-k/increase-s-k.Rmd
Include k = 5 in increase-s-k notebook #22

```{r}
k_seq <- seq(1, 15, by = 2)
s_seq <- 1:10

@@

# Assume anything more than a million isn't possible
M[M > 1e6] <- NA
```

@@

We start by reading in a selection of fitted PCA-AGHQ models.
We only need the quadrature part of the returned object:

@@

read_sk(s = 1, k = 3)
read_sk(s = 2, k = 3)
read_sk(s = 3, k = 3)
read_sk(s = 4, k = 3)
read_sk(s = 5, k = 3)
```

Check that a few of the runs have the correct number of grid points:

```{r}
stopifnot(nrow(s5k2$quad$modesandhessians) == 2^5)
stopifnot(nrow(s3k3$quad$modesandhessians) == 3^3)
```

@@

```{r}
k2 <- list(s1k2, s2k2, s3k2, s4k2, s5k2)
k3 <- list(s1k3, s2k3, s3k3, s4k2, s5k3)

df <- data.frame(
  s = rep(1:5, times = 2),
  k = rep(2:3, each = 5),
  lognormconst = sapply(c(k2, k3), function(x) x$quad$normalized_posterior$lognormconst),
  time = sapply(c(k2, k3), function(x) x$time)
)

>>>>

```{r}
k_seq <- 1:10
s_seq <- 1:10

@@

# Assume anything more than a million isn't possible
M[M > 1e6] <- NA

M
```

@@

We start by reading in a selection of fitted PCA-AGHQ models.
We only need certain parts of the fits, and as they are large we are careful here with memory.

@@

stopifnot(nrow(s5k2$quad$modesandhessians) == 2^5)

k2 <- list(s1k2, s2k2, s3k2, s4k2, s5k2)
k2_lognormconsts <- sapply(k2, function(x) x$quad$normalized_posterior$lognormconst)
k2_times <- sapply(k2, function(x) x$time)

rm(list = c("k2", "s1k2", "s2k2", "s3k2", "s4k2", "s5k2"))
gc()

read_sk(s = 1, k = 3)
read_sk(s = 2, k = 3)
read_sk(s = 3, k = 3)
read_sk(s = 4, k = 3)
read_sk(s = 5, k = 3)

stopifnot(nrow(s3k3$quad$modesandhessians) == 3^3)

k3 <- list(s1k3, s2k3, s3k3, s4k3, s5k3)
k3_lognormconsts <- sapply(k3, function(x) x$quad$normalized_posterior$lognormconst)
k3_times <- sapply(k3, function(x) x$time)

rm(list = c("k3", "s1k3", "s2k3", "s3k3", "s4k3", "s5k3"))
gc()

read_sk(s = 1, k = 5)
read_sk(s = 2, k = 5)
read_sk(s = 3, k = 5)
read_sk(s = 4, k = 5)
read_sk(s = 5, k = 5)

k5 <- list(s1k5, s2k5, s3k5, s4k5, s5k5)
k5_lognormconsts <- sapply(k5, function(x) x$quad$normalized_posterior$lognormconst)
k5_times <- sapply(k5, function(x) x$time)

rm(list = c("k5", "s1k5", "s2k5", "s3k5", "s4k5", "s5k5"))
gc()
```

@@

```{r}
df <- data.frame(
  s = rep(1:5, times = 3),
  k = rep(c(2, 3, 5), each = 5),
  lognormconst = c(k2_lognormconsts, k3_lognormconsts, k5_lognormconsts),
  time = c(k2_times, k3_times, k5_times),
)
